\chapter{Regression + Classification}
Consider the marks information: \\
L1\textunderscore MARKS, L2\textunderscore MARKS, L3\textunderscore MARKS, S1\textunderscore MARKS, S2\textunderscore MARKS, S3\textunderscore MARKS. Consider TOTAL\textunderscore MARKS as the dependent variable
\begin{itemize}
	\item
	Objective:
	\begin{itemize}
		\item
		Determine the least number of attributes S that give the best possible regression equation (least error)
		\item
		Build a classification model based on S for NRC\textunderscore CLASS class variable
	\end{itemize}
	
	\item
	Procedure followed: 
	\begin{itemize}
		\item
		Data is loaded and cleansed by removing invalid and missing rows.
		\item
		Regression analysis is performed on the data by using the marks data.
		\item
		Synergy/Interaction effect of all the marks are obsereved and the combination of marks having least p-value is chosen for classification.
		\item
		Marks are rounded off for improving the speed of classification.
		\item
		Classification is performed on the data based on the class variable combination having least p-value.
		\item
		The results of confusion matrices are compared.
	\end{itemize}
	
	\item
	Results Obtained:
	\begin{itemize}
		\item
		All Subjects are used for classification:
		\begin{itemize}
			\item
			Accuracy: 90.2\%
			\item
			95\% CI: (0.8962, 0.9076)
		\end{itemize}
		
		\item
		Best case: \\	
		L1\textunderscore MARKS, L2\textunderscore MARKS, S2\textunderscore MARKS, S3\textunderscore MARKS (p-value = 0.0732) are used for classification:
		\begin{itemize}
			\item
			Accuracy: 84.03\%
			\item
			95\% CI: (0.8332, 0.8472)
		\end{itemize}
		
		\item
		Worst case: \\
		L3\textunderscore MARKS, S1\textunderscore MARKS (p-value = 0.94523) are used for classification:
		\begin{itemize}
			\item
			Accuracy: 69.46\%
			\item
			95\% CI: (0.6857, 0.7033)
		\end{itemize}
	\end{itemize}
	
	\item
	Conclusion:
	\begin{itemize}
		\item
		Taking all the subjects marks for classification gives the highest accuracy.
		\item
		Taking the combination of the subjects having low p-value offers the next highest accuracy for classification.
		\item
		Conversely, the combination of subjects having highest p-value gives the least accuracy.
	\end{itemize}
\end{itemize}